DynaProg for Scala

### 2013-01-06 docs/report/report.tex
Added host memory fallback, nits in code.

\section{Future work} \ul
\item Implementation for serial problems larger than memory, using hybrid (Myers and Miller's algorithm with $\log_k$ with $k$ depending on available memory)
\item Transforming non-serial into serial using aggregation functions/transformations
\item Avoid to maintain the cost matrix in memory by moving data in the wavefront
\item Non-serial scheduling for large problems (with memory loads for non-serializable)
\item Add FPGA target platform (George Nithin)
\item Pack the data => less memory transfer (i.e. GATC=>4 letters in 1 char)
\item Operate on larger words (ex 64 bits) to increase thread locality and reduce memory accesses
\ule

>>>>

Compare current implementation versus ad-hoc implementation. Compare CUDA vs Scala (we might need to ad-hoc fix stack overflows in Scala).
If Zuker coefficients can be fixed, compare performance with \cite{adp_gpu} by rescaling numbers wrt to bandwidth and computation performance.

\section{Future work}
We consider several directions and possible extensions for our work. We briefly describe each of them and give an idea of how they could be implemented:\ol
\item \textbf{Non-serial scheduling for problems larger than the device memory:} as described in \ref{ns_mem_transfer}, it could be possible to handle problems that are larger than the device memory in a general context, with the extra penalties of memory transfers between main and device memory and a more complex indexing strategy (since we need to find the matrix block in which lies the data, then address the element within the block.

Since recent CUDA devices implement the possibility to address host memory directly from the device, a simple change in the memory allocation strategy could allow larger problems to be solved within the main memory instead of the GPU memory. However, a more thorough analysis on the addressing cost and load penalties should be done to decide which of the strategy is the best.

{\color{red} XXX: need to force 64 bits mode -m64}

% http://www.opensource.apple.com/source/xnu/xnu-2050.18.24/osfmk/vm/vm_map.c : add_wire_counts

 large problems (with memory loads for non-serializable)
\ole

 \ul
\item Implementation for serial problems larger than memory, using hybrid (Myers and Miller's algorithm with $\log_k$ with $k$ depending on available memory)
\item Transforming non-serial into serial using aggregation functions/transformations
\item Avoid to maintain the cost matrix in memory by moving data in the wavefront
\item 
\item Add FPGA target platform (George Nithin)
\item Pack the data => less memory transfer (i.e. GATC=>4 letters in 1 char)
\item Operate on larger words (ex 64 bits) to increase thread locality and reduce memory accesses
\ule
